---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mplush5

<!-- badges: start -->

<!-- badges: end -->

A new feature of Mplus is the ability to have the results saved to an external (hdf5) file that can then be used in other statistical programs. An hdf5 file is a hierarchical data format that is able to store large amounts of data.

It is possible to read a hdf5 file directly into R (using the `rhdf5` library) but it can be difficult to navigate around the file and find the desired results. Thuy Nguyen of Muthen & Muthen wrote a series of functions that make it easier to access the results of the hdf5 file. These functions were saved in two `.R` files that would need to be downloaded from the web and sourced in R before they could be used. This made it difficult to use these functions when collaborating with others.

The goal of `mplush5` is to put these functions into a R package so that it becomes easier to use these functions in collaboration with others.

The original files can be found at <https://www.statmodel.com/mplus-R/H5Results.zip>.

## Installation

You can install the development version of `mplush5` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dougtommet/mplush5")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mplush5)
## basic example code
# h5_path <- path_to_h5_file
# mplus.view.results(h5_path)
# mplus.print.model.results(h5_path)
```
